Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
skolem fct wording
Time bound

Theorem~\ref{thm:synth-semicomplete} provides a time bound -- the CEGIS loop can iterate at most
$2^bk$ times and each iteration requires solving 2 NP-complete problems of size < $2^bk \times \| L\|$
with $\| L \| $ the size of the program-under-analysis computing $\| L \|$.  So the
runtime is bounded by $2^{bk+1} NP(2^bk \| L \|)$.

>>>>

Theorem~\ref{thm:synth-semicomplete} provides a time bound -- the CEGIS loop can iterate at most
$2^bk$ times where $k$ is the number of variables used by $L$ and
$b$ is the number of bits used to store each variable.
The $i$th iteration of the loop requires solving 2 NP-complete problems of size $i \times \| L\|$
with $\| L \| $ the size of the program-under-analysis computing $\| L \|$.  So if 
the CEGIS loop iterates $n$ times, the
runtime is bounded by $2 \times n \times NP(n \times \| L \|)$, which is bounded
by $2^{bk + 1} NP(2^{bk} \| L \|)$.  Clearly the runtime is affected most strongly by $n$,
the total number of iterations of the CEGIS loop.
